### 2021-07-07 msgauge-intro.tex
Section 1 almost done.

\begin{document}
\outline
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Symplectic geometry (mechanical perspective)}
\begin{columns}[T]
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "geometric approach" to mechanics \dots}
		%
		\begin{columns}
			\begin{column}{.60\linewidth}
				\begin{center}
					\includegraphics[width=0.6\linewidth]{Pictures/pendulum13}			
				\end{center}
			\end{column}	
			\begin{column}{.40\linewidth}
				\begin{center}
					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
				\end{center}
			\end{column}	
		\end{columns}
		%
		\begin{defblock}[Symplectic Manifold]
			\vspace{-1em}
			\includestandalone[width=1\textwidth]{Pictures/Figure_sym}	
		\end{defblock}
		%
		\pause
		\begin{exblock}[$M = T^\ast Q$ is symplectic]
			$\omega = d \theta $ with
			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
		\end{exblock}
		%
		\pause
		\vspace{1em}
		\centering
		\textit{ based on the notion of "states".}		
	\end{column}
	\onslide<1->{\vrule{}}
	\pause
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "algebraic approach" to mechanics \dots}
		\vspace{.5em}	
		\begin{defblock}[Classical Observables]
			Unital, associative, commutative algebra $C^\infty(M)$.
		\end{defblock}
		%
		\vspace{.5em}
		\pause
		\begin{defblock}[Hamiltonian vector fields]
			$v_f \in \mathfrak{X}(M)$ such that:
			$$\iota_{v_f} \omega = -df \quad \text{(exact)}$$ %$\in B^1(M)$
			\small$v_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.
		\end{defblock}
		%
		\begin{defblock}[Poisson Algebra of Observables]
			$C^\infty(M)$ is a Poisson algebra with
			$$\{f,g\} = \iota_{v_g} \iota_{v_f} \omega = \omega(v_f,v_g) ~.$$
		\end{defblock}
		%
		\pause
		\vspace{.8em}
		\centering
		\textit{ based on the notion of "meaurable quantities".}						
	\end{column}
\end{columns}
\end{frame}
\note[itemize]{
	\footnotesize

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{From Symplectic to MultiSymplectic (mechanical perspective)}
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[•] Kijowski and W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
	\end{block}
	\vfill
	\begin{center}
	\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
		\alert{
		\faWarning \qquad
			{The lack of a satisfactory notion of observables hindered the spread of this formalism.}	
		\qquad \faWarning		
		}
	}
	\end{center}

	\vfill
	\begin{center}
	\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
		\alert{
		\faQuestionCircle \qquad
			{Why observables are so crucial?\qquad \qquad Quantization!}	
		\qquad \faQuestionCircle		
		}
	}
	\end{center}

>>>>

\begin{document}
\outline
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Symplectic geometry (mechanical perspective)}
\begin{columns}[T]
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "geometric approach" to mechanics \dots}
		%
		\begin{columns}
			\begin{column}{.60\linewidth}
				\begin{center}
					\includegraphics[width=0.6\linewidth]{Pictures/pendulum13}			
				\end{center}
			\end{column}	
			\begin{column}{.40\linewidth}
				\begin{center}
					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
				\end{center}
			\end{column}	
		\end{columns}
		%
		\begin{defblock}[Symplectic Manifold]
			\vspace{-1em}
			\includestandalone[width=1\textwidth]{Pictures/Figure_sym}	
		\end{defblock}
		%
		\pause
		\begin{exblock}[$M = T^\ast Q$ is symplectic]
			with $\omega = d \theta $ given by
			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
		\end{exblock}
		%
		\pause
		\vspace{1em}
		\centering
		\textit{ based on the notion of "states".}		
	\end{column}
	\onslide<1->{\vrule{}}
	\pause
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "algebraic approach" to mechanics \dots}
		\vspace{.5em}	
		\begin{defblock}[Classical Observables]
			Unital, associative, commutative algebra $C^\infty(M)$.
		\end{defblock}
		%
		\vspace{.5em}
		\pause
		\begin{defblock}[Hamiltonian vector fields]
			$v_f \in \mathfrak{X}(M)$ such that:
			$$\iota_{v_f} \omega = -df \quad \text{(exact)}$$ %$\in B^1(M)$
			\small$v_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.
		\end{defblock}
		%
		\begin{defblock}[Poisson Algebra of Observables]
			$C^\infty(M)$ is a Poisson algebra with
			$$\{f,g\} = \iota_{v_g} \iota_{v_f} \omega = \omega(v_f,v_g) ~.$$
		\end{defblock}
		%
		\pause
		\vspace{.8em}
		\centering
		\textit{ based on the notion of "meaurable quantities".}						
	\end{column}
\end{columns}
\end{frame}
\note[itemize]{
	\footnotesize

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{From Symplectic to MultiSymplectic (mechanical perspective)}
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[•] Kijowski and W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
	\end{block}
	\vfill
	\pause
	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]
		\color{red}
		\begin{columns}[T]
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faWarning
				\end{center}
			\end{column}			
			\begin{column}{.60\linewidth}
				\begin{center}
					The lack of a satisfactory notion of observables hindered the spread of this formalism.
				\end{center}
			\end{column}			
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faWarning
				\end{center}
			\end{column}			
		\end{columns}
	\end{tcolorbox}
	\vfill
	\pause
	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue,dashed}]
		\color{blue}
		\begin{columns}[T]
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faQuestionCircle
				\end{center}
			\end{column}			
			\begin{column}{.60\linewidth}
				\begin{center}
					{Why observables are so crucial?\qquad \qquad Quantization!}	
				\end{center}
			\end{column}			
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faQuestionCircle
				\end{center}
			\end{column}			
		\end{columns}
	\end{tcolorbox}
